SNIK: Textbook Knowledge on Hospital Information Management as Linked Data

### 2021-08-20 paper.tex
Update paper.

\section{Future Work}
\todo{Connection with HITO}
We plan to extend the text-based interlinks with semantic-similarity-based ontology matching [5] to find more correspondencies between the textbooks.
This will enable users to switch to another textbook when a certain concept is explained there in more detail.
The SNIK toolset, SNIK Graph in particular, is under permanent improvement.
For instance, we are considering alternatives to the shortest path that are the most preferred by different audiences and whether those paths can be (semi-)automatically generated using suitable node or edge weight functions.
We are also investigating candidates for additional subontologies and as interlink targets.

>>>>

\section{Future Work}
We plan to extend the text-based interlinks with semantic-similarity-based ontology matching [5] to find more correspondencies between the textbooks.
This will enable users to switch to another textbook when a certain concept is explained there in more detail.
The SNIK toolset, SNIK Graph in particular, is under permanent improvement.
For instance, we are considering alternatives to the shortest path that are the most preferred by different audiences and whether those paths can be (semi-)automatically generated using suitable node or edge weight functions.
We are also investigating candidates for additional subontologies and as interlink targets.

Past efforts of automatic textbook extractions were unsuccessfull but recent advances in natural language processing, such as GPT-3~\citep{gpt3}, motivate further investigation.
